Title Goes Here

### 2017-08-16 analysis/paper/paper.Rmd
separate the code into several chunks

library(datacitation)
```

@@

library(rdatacite)
# dc_arch <- dc_search(q = "archaeology", rows = pretty(100000)[2])
# saveRDS(dc_arch, "dc_arch.rds")
dc_arch <- readRDS("dc_arch.rds")

library(tidyverse)
library(stringr)
glimpse(dc_arch)

dc_arch <- 
dc_arch %>% 
mutate(the_text =  toupper(gsub(" |_|\\(|\\)", "-", rights)),
       the_text = gsub("(\\-)\\1+", "\\1", the_text),
       the_text = gsub("-$", "", the_text)) %>% 
  mutate(cc = case_when(
    grepl("SEMANTICS/OPENACCESS", the_text) ~ "EU Open Access",
    grepl("SEMANTICS/RESTRICTEDACCESS", the_text) ~ "EU Restricted Access",
    grepl("SEMANTICS/CLOSEDACCESS", the_text) ~ "EU Closed Access",
    grepl("CC-BY-[^NC-ND]|CC-BY$|ATTRIBUTION-LICENSE|ATTRIBUTION-[^NON]", the_text) ~ "CC-BY",
    grepl("CC-BY-NC-[^ND]|BY-NC-[^ND]|CC-NC$|ATTRIBUTION-NON-COMMERCIAL-", the_text) ~ "CC-BY-NC",
    grepl("CC-BY-NC-SA-[^ND]|CC-NC-SA$|ATTRIBUTION-NON-COMMERCIAL-SHARE", the_text) ~ "CC-BY-NC-SA",
    grepl("CC-BY-NC-ND|BY-NC-ND|ATTRIBUTION-NONCOMMERCIAL-NO-DERIVATIVE|ATTRIBUTION-NONCOMMERCIAL-NODERIVATIVES|ATTRIBUTION-NONCOMMERCIAL-NODERIVS|NAMENSNENNUNG-NICHTKOMMERZIELL-KEINEBEARBEITUNG|NAMENSNENNUNG-KEINE-KOMMERZIELLE-NUTZUNG", the_text) ~ "CC-BY-NC-ND",
    grepl("ADS|ARCHAEOLOGYDATASERVICE", the_text) ~ "ADS",
    grepl("CC0|CC-0|ZERO", the_text) ~ "CC-0"
  )) %>% 
  mutate(yyyy_created =  as.numeric(substr(created, 1,4)),
         yyyy_date =  as.numeric(substr(date, 1,4)))

@@

# clean up rights a bit

theme_new <- function(base_size = 12){
  theme_bw(base_size = base_size) %+replace%
    theme(
      #axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      axis.title = element_text(size = 14),
      legend.key=element_rect(colour=NA, fill =NA),
      # panel.grid = element_blank(),   
      panel.border = element_rect(fill = NA, colour = "black", size=0.5),
      panel.background = element_rect(fill = "white", colour = "black"), 
      strip.background = element_rect(fill = NA)
    )
}

@@

library(plotly)
ggplotly(date_plot)

@@

why_2008 <- 
  xx %>% 
  filter(as.numeric(substr(date, 1,4)) == 2008) %>% 
  group_by(publisher) %>% 
  tally(sort = TRUE)

# panel of plots
# combine plots for lang and data center
datacentre_and_langugage_plot <- 
  datacentre_plot + annotation_custom(ggplotGrob(language_plot),
                                      xmin = 1.15, 
                                      xmax = 6.15,
                                      ymin = 10000,
                                      ymax = 40000
  )

@@

@@

datacentre_rights_table[1:11,] %>% 
  ggplot(aes(cc, datacentre)) + 
  geom_point(aes(size = n),
             colour = "grey80") +
  theme_bw() + 
  xlab("") + 
  ylab("") +
  scale_size_continuous(range=c(5,25)) + 
  geom_text(aes(label = n))

>>>>

library(datacitation)

theme_new <- function(base_size = 12){
  theme_bw(base_size = base_size) %+replace%
    theme(
      #axis.title.x=element_blank(),
      # axis.title.y=element_blank(),
      axis.title = element_text(size = 14),
      legend.key=element_rect(colour=NA, fill =NA),
      # panel.grid = element_blank(),   
      panel.border = element_rect(fill = NA, colour = "black", size=0.5),
      panel.background = element_rect(fill = "white", colour = "black"), 
      strip.background = element_rect(fill = NA)
    )
}
```

@@

library(rdatacite)
# dc_arch <- dc_search(q = "archaeology", rows = pretty(100000)[2])
# saveRDS(dc_arch, "dc_arch.rds")
dc_arch <- readRDS("C:\\emacs\\dc_arch.rds")

library(tidyverse)
library(stringr)
# glimpse(dc_arch)

dc_arch <- 
dc_arch %>% 
mutate(the_text =  toupper(gsub(" |_|\\(|\\)", "-", rights)),
       the_text = gsub("(\\-)\\1+", "\\1", the_text),
       the_text = gsub("-$", "", the_text)) %>% 
  mutate(cc = case_when(
    grepl("SEMANTICS/OPENACCESS", the_text) ~ "EU Open Access",
    grepl("SEMANTICS/RESTRICTEDACCESS", the_text) ~ "EU Restricted Access",
    grepl("SEMANTICS/CLOSEDACCESS", the_text) ~ "EU Closed Access",
    grepl("CC-BY-[^NC-ND]|CC-BY$|ATTRIBUTION-LICENSE|ATTRIBUTION-[^NON]", the_text) ~ "CC-BY",
    grepl("CC-BY-NC-[^ND]|BY-NC-[^ND]|CC-NC$|ATTRIBUTION-NON-COMMERCIAL-", the_text) ~ "CC-BY-NC",
    grepl("CC-BY-NC-SA-[^ND]|CC-NC-SA$|ATTRIBUTION-NON-COMMERCIAL-SHARE", the_text) ~ "CC-BY-NC-SA",
    grepl("CC-BY-NC-ND|BY-NC-ND|ATTRIBUTION-NONCOMMERCIAL-NO-DERIVATIVE|ATTRIBUTION-NONCOMMERCIAL-NODERIVATIVES|ATTRIBUTION-NONCOMMERCIAL-NODERIVS|NAMENSNENNUNG-NICHTKOMMERZIELL-KEINEBEARBEITUNG|NAMENSNENNUNG-KEINE-KOMMERZIELLE-NUTZUNG", the_text) ~ "CC-BY-NC-ND",
    grepl("ADS|ARCHAEOLOGYDATASERVICE", the_text) ~ "ADS",
    grepl("CC0|CC-0|ZERO", the_text) ~ "CC-0"
  )) %>% 
  mutate(yyyy_created =  as.numeric(substr(created, 1,4)),
         yyyy_date =  as.numeric(substr(date, 1,4)))
```

```{r}

@@

```{r}

@@

library(plotly)
ggplotly(date_plot)
```

```{r}

@@

why_2008 <- 
  xx %>% 
  filter(as.numeric(substr(date, 1,4)) == 2008) %>% 
  group_by(publisher) %>% 
  tally(sort = TRUE)
```

```{r}
# panel of plots
# combine plots for lang and data center
datacentre_and_langugage_plot <- 
  datacentre_plot + annotation_custom(ggplotGrob(language_plot),
                                      xmin = 1.15, 
                                      xmax = 6.15,
                                      ymin = 10000,
                                      ymax = 40000
  )

@@

```{r}

@@

datacentre_rights_table[1:11,] %>% 
  ggplot(aes(cc, datacentre)) + 
  geom_point(aes(size = n),
             colour = "grey80") +
  theme_bw() + 
  xlab("") + 
  ylab("") +
  scale_size_continuous(range=c(5,25)) + 
  geom_text(aes(label = n)) +
  theme(legend.position = "none")
